The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-26 design.tex
re structure

Specifically, a simple instance with configuration \autoref{tab:simpleresourceconfiguration}--\ref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple resource configuration}
    \begin{tabular}{ccc}
    \toprule
    Resource & Type  & Capacity \\
    \midrule
    $r_1$ & 1     & 10 \\
    $r_2$ & 2     & 10 \\
    $r_3$ & 3     & 10 \\
    $r_4$ & 3     & 10 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simpleresourceconfiguration}%
\end{table}%
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources}
	\label{fig:scheduleChart}
\end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

@@

\begin{table}[htbp]
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

@@

\begin{gather}
\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
Rank_m, \mathcal{L}_m \right) \\ 
\text{s.t.}\notag
\end{gather}
\begin{numcases}{}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)\right) & \\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
m \in \left\{ l^*,\bm{k}^* \right\} 
\end{numcases}

@@

The assignment of new service-call will not driven these decision making event because of the resource capacity consuming feature, so it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job come after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.  
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/service-call}}
	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
	\label{fig:simplejoblist}
\end{figure}
Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$

@@

We will ignore resource type subscript $\alpha$ here for the reason that resources perform the task already meet the type needs. With the assumption given above, higher resource occupation($p_{ij}\cdot q_{ij}$), lower delay($f_{ij} - p_{ij} - r_{ij}$), larger difference between actual and expected product quality($\delta_{ij}-\gamma_{ij}$), will turn out higher rank value($rank$) changing:
\begin{subnumcases}{}
rank := rank +
\frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} &\\
\delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
\end{subnumcases}

@@

This decision making is a control method for platform to keep the performance of tasks with content quality and efficiency. We denote the list of all resources with type $\alpha$ as $\bm{mr}_\alpha$ and the list of all services as $\bm{ms}$ at time $\tau$, after the sort these lists according to the scarcity and quality, the unqualified resources and services. Scarcity can be defined as:
\begin{subnumcases}{}
\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} } & $\alpha\in\mathcal{A}$ \label{eq:resourcescarcity}\\ 
\abs{\mathcal{L}_{l,\tau}} \label{eq:servicescarcity}
\end{subnumcases}

@@

\subsection{Tricky problems} % (fold)
\label{sub:tricky_problems}
Even though the schedule mode exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed. Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock}, 
\begin{figure}[htbp]
	\centering
	\resizebox{.85\textwidth}{!}{\input{figures/job-lock}}
	\caption{Simple illustration of job lock problem}
	\label{fig:joblock}
\end{figure}
$t_{i2}$ is active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is active in $mr_1$ and inactive in $mr_2$, because of the capacity limit, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and will they will block the other tasks from being processed.

>>>>

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
% \begin{table}[htbp]
%   \centering
%   \scriptsize
%   \caption{Simple resource configuration}
%     \begin{tabular}{ccc}
%     \toprule
%     Resource & Type  & Capacity \\
%     \midrule
%     $r_1$ & 1     & 10 \\
%     $r_2$ & 2     & 10 \\
%     $r_3$ & 3     & 10 \\
%     $r_4$ & 3     & 10 \\
%     \bottomrule
%     \end{tabular}%
%   \label{tab:simpleresourceconfiguration}%
% \end{table}%
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources}
	\label{fig:scheduleChart}
\end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

@@

\begin{table}[htbp]
  \scriptsize
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

@@

\begin{equation}
\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
Rank_m, \mathcal{L}_m \right) \\ 
% \text{s.t.}\notag
\end{equation}
\begin{numcases}{\text{s.t.}}
% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)\right) & \\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
m \in \left\{ l^*,\bm{k}^* \right\} 
\end{numcases}

@@

The assignment of new service-call will not driven these decision making event because of the resource capacity consuming feature, so it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job come after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.  
\begin{figure}[htbp]
	\centering
	\resizebox{.75\textwidth}{!}{\input{figures/service-call}}
	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
	\label{fig:simplejoblist}
\end{figure}
Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$

@@

We will ignore resource type subscript $\alpha$ here for the reason that resources perform the task already meet the type needs. With the assumption given above, higher resource occupation($p_{ij}\cdot q_{ij}$), lower delay($f_{ij} - p_{ij} - r_{ij}$), larger difference between actual and expected product quality($\delta_{ij}-\gamma_{ij}$), will turn out higher rank value($rank$) changing:
\begin{subnumcases}{}
rank := rank +
\frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} & \\
\delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
\end{subnumcases}

@@

This decision making is a control method for platform to keep the performance of tasks with content quality and efficiency. We denote the list of all resources with type $\alpha$ as $\bm{mr}_\alpha$ and the list of all services as $\bm{ms}$ at time $\tau$, after the sort these lists according to the scarcity and quality, the unqualified resources and services. Scarcity can be defined as:

\begin{subnumcases}{}
\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} } & $\alpha\in\mathcal{A}$ \label{eq:resourcescarcity}\\ 
\abs{\mathcal{L}_{l,\tau}} & \label{eq:servicescarcity}
\end{subnumcases}

@@

\subsection{Tricky problems} % (fold)
\label{sub:tricky_problems}
Even though the schedule mode exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed. Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock}, 
\begin{figure}[htbp]
	\centering
	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
	\caption{Simple illustration of job lock problem}
	\label{fig:joblock}
\end{figure}
$t_{i2}$ is active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is active in $mr_1$ and inactive in $mr_2$, because of the capacity limit, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and will they will block the other tasks from being processed.

### 2016-08-26 figures/scheduleChart.tex
re structure

\begin{tikzpicture}
\foreach \x in {0,6,12,18}
	\draw [->,thick] (15.7cm,\x cm) node{t} (0,\x cm) -- +(15.5cm, 0) ;
\foreach \x in {0,6,12,18}
	\draw [->,thick] (0,\x cm) -- +(0,5.2 cm);
\foreach \x in {0,6,12,18}
	\draw[yshift=5.35cm] (0,\x cm) node{Capacity};
\foreach \x in {1,2,3,4}
	\draw[yshift=23.5cm] (7.5cm,-6*\x cm) node{$r_\x$};
\foreach \x in {1,...,15}
	\foreach \y in {0,6,12,18}
		\draw (\x cm,\y cm) -- +(0,2mm);
\foreach \x in {1,...,15}
	\foreach \y in {0,6,12,18}
		\draw[yshift=-2mm] (\x cm,\y cm) node{$\x$};
\foreach \y in {0,6,12,18}
	\foreach \x in {1,...,10}
		\draw[yshift=\y cm] (0,0.5*\x cm) -- +(2mm,0) (-3mm,0.5*\x cm) node{$\x$};

\fill[blue!20!,yshift=18cm] (6cm,4cm) rectangle (7cm,5cm);
\draw[yshift=18cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
\draw[dotted,yshift=18cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
\draw[yshift=12cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
\draw[dotted,yshift=12cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
\draw[dotted,yshift=6cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}

>>>>

\begin{tikzpicture}
\foreach \x in {0,6.5,13,19.5}
	\draw [->,thick] (15.7cm,\x cm) node{t} (0,\x cm) -- +(15.5cm, 0) ;
\foreach \x in {0,6.5,13,19.5}
	\draw [->,thick] (0,\x cm) -- +(0,5.2 cm);
\foreach \x in {0,6.5,13,19.5}
	\draw[yshift=5.35cm] (0,\x cm) node{Capacity};
\foreach \x in {1,...,15}
	\foreach \y in {0,6.5,13,19.5}
		\draw (\x cm,\y cm) -- +(0,2mm);
\foreach \x in {1,...,15}
	\foreach \y in {0,6.5,13,19.5}
		\draw[yshift=-2mm] (\x cm,\y cm) node{$\x$};
\foreach \y in {0,6.5,13,19.5}
	\foreach \x in {1,...,10}
		\draw[yshift=\y cm] (0,0.5*\x cm) -- +(2mm,0) (-3mm,0.5*\x cm) node{$\x$};

\draw (7.5cm,-7mm) node{$r_4$, initial capacity = 10, type = 3};
\draw[yshift=6.5cm] (7.5cm,-7mm) node{$r_3$, initial capacity = 10, type = 3};
\draw[yshift=13cm] (7.5cm,-7mm) node{$r_2$, initial capacity = 10, type = 2};
\draw[yshift=19.5cm] (7.5cm,-7mm) node{$r_1$, initial capacity = 10, type = 1};

\fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
\draw[dotted,yshift=19.5cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}
